---
title: 'Exercise #2'
author: "Felix Radtke"
date: "date of submission"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# more internal settings can go here
# Consider help pages like:
# https://rmarkdown.rstudio.com/lesson-1.html
# https://www.rstudio.com/wp-content/uploads/2015/03/rmarkdown-reference.pdf

```

### Loaded packages

```{r libraries}
# Load all packages here, consider to mute output of this code chunk
# https://rmarkdown.rstudio.com/lesson-3.html
library(tidyverse)
library(lubridate)
library(zoo)
```

### Preprocessing / R functions

```{r preprocessing_or_functions, message=FALSE, warning=FALSE}
# If data preprocessing is needed, do it here.
# If you have specific functions, placed them here.
# If this code chunk is not needed, delete it.
meanNA <- function(x){mean(x, na.rm = TRUE)}

```

## 1. Quality control procedures (4 QCPs)

```{r, eval = FALSE}
# Load data from Github (then eval = TRUE)
data_10min <- read_csv(file = 'https://raw.githubusercontent.com/data-hydenv/data/master/hobo/2022/10_minute/10347355.csv',  col_names = T) 
head(data)
```

### 1.1 Measurement range (Plausible values)

```{r qcp1, eval = FALSE}
# code for qcp2 here, e.g.: (set eval = TRUE to activate the code chunk)
data_10min_QC1 <- data_10min %>% 
	mutate(qc1 = if_else(between(temp, -20, 70), 0, 1))

sum(data_10min_QC1$qc1, na.rm = T)
```

**Question**: How many data points are outside the measurement range?

**Answer**:
0 Points are outside the measurement range

### 1.2 Plausible rate of change

```{r qcp2}
data_10min_QC2 <- data_10min_QC1 %>% 
	mutate(qc2 = if_else(lag(temp) > (temp + 1) | lag(temp) < (temp - 1), 1, 0))

sum(data_10min_QC2$qc2, na.rm = T)
```

**Question**: Describe shortly how many data points failed during this QCP and discuss whether there is a certain daytime pattern of failure or not?

**Answer**:

### 1.3 Minimum variability (Persistence)

```{r qcp3}
data_10min_QC3 <- data_10min_QC2 %>% 
	mutate(qc3_V1 = lag(temp, n = 1)) %>% 
	mutate(qc3_V2 = lag(temp, n = 2)) %>% 
	mutate(qc3_V3 = lag(temp, n = 3)) %>% 
	mutate(qc3_V4 = lag(temp, n = 4)) %>% 
	mutate(qc3_V5 = lag(temp, n = 5)) %>% 
	
	mutate(qc3 = if_else(qc3_V1 == temp & qc3_V2 == temp & qc3_V3 == temp & qc3_V4 == temp & qc3_V5 == temp, 1, 0)) %>% 
	select(id, dttm, temp, lux, qc1, qc2, qc3)

sum(data_10min_QC3$qc3, na.rm = T)
```

**Task**: Code in this section should analyses the persistance.

### 1.4 Light intensity

```{r qcp4}
data_10min_QC4 <- data_10min_QC3 %>% 
	mutate(SIC_class = case_when(
		between(lux, 0, 10) ~ "night",
		between(lux, 10, 500) ~ "dawn",
		between(lux, 500, 2000) ~ "overcast_full",
		between(lux, 2000, 15000) ~ "overcast_light",
		between(lux, 15000, 20000) ~ "clear_sky",
		between(lux, 20000, 50000) ~ "sunshine",
		lux > 50000 ~ "sunshine_bright",
	)) %>% 
	mutate(time = substring(dttm, 12, 20)) %>% 
	mutate(day_night = if_else(between(as.numeric(as.POSIXct(time, format="%H:%M:%S")),
					   as.numeric(as.POSIXct('06:00:00', format="%H:%M:%S")), 
					   as.numeric(as.POSIXct('17:59:59', format="%H:%M:%S"))), 
				   "day","night")) %>% 
	# transform time to milliseconds, depending on the actual day


	mutate(lux_sun = if_else(SIC_class == "sunshine" & day_night == "day", 1, 0),
	       lux_sun = rollapply(lux_sun, width = 3, FUN = sum, fill = NA),
	       lux_sunbright = if_else(SIC_class == "sunshine_bright" & day_night == "day", 1, 0),
	       lux_sunbright = rollapply(lux_sunbright, width = 7, FUN = sum, fill = NA),
	       qc4 = if_else(lux_sun > 0 | lux_sunbright > 0, 1, 0)) %>% 
	select(id, dttm, temp, lux, qc1, qc2, qc3, qc4)

sum(data_10min_QC4$qc4, na.rm = T)
```

**Task**: Discuss shortly how often and when during daytime the QCP4 flags bad data. Elaborate on some reasons for your results.

**Answer**:

## 2. Synthesis

```{r synthesis}
# code for synthesis here
```

**Task**: Present a table or graph to show how many data points fail during the four specific QCPs. Discuss shortly the reasons for failure and compare the different QCPs against each other.

**Answer**:

## 3. Results

### 3.1 Result (Flagging system: 10-minutes-values)

```{r res1}
qc_df <- data_10min_QC4 %>% 
	mutate(qc_total = qc1 + qc2 + qc3 + qc4) %>% 
	select(id, dttm, temp, lux, qc1, qc2, qc3, qc4, qc_total)
```

**Task**: At the end of the code section above you should generate one! tibble or data.frame named `qc_df` with all time information, all data points (temperature and lux) and your outcomes of the different QCPs.

### 3.2 Result (Aggregate to hourly series)

```{r res2}
data_hourly_pre <- qc_df %>% 
	mutate(dttm = floor_date(dttm, 'hour')) %>% 
	group_by(dttm) %>% 
	summarise(th = round(meanNA(temp), 3),
		  lux = round(meanNA(lux), 3),
		  qc1 = sum(qc1),
		  qc2 = sum(qc2),
		  qc3 = sum(qc3),
		  qc4 = sum(qc4),
		  qc_total = sum(qc_total)) %>% 
	rename(date_time = dttm) %>% 
	ungroup() 

# hours with more than one flag will be declared as NA
data_hourly_pre$th[which(data_hourly_pre$qc_total > 1)] <- NA

# delete all not needed collums
data_hourly <- data_hourly_pre %>% 
	select(date_time, th)
```

**Task**: At the end of the code section above you should generate one! tibble or data.frame named `hobo_hourly` with averaged temperature values per hour or NA values (if the hour is flagged as bad data). See exercise description for more details.

-   First column: YYYY-DD-MM HH:MM:SS

-   Second column: Temperature values (4 digits), NA values possible
